Spec2Fab: A High-Fidelity Mapping from Specification to Fabrication

### 2012-12-20 paper.tex
digram

\subsection{Optimizer}
\begin{enumerate}
\item MCMC, Simulated Anealing, SPSA
\item Branch and bound (plus clustering of similar configurations)
\item (Optional) reinforcement learning, deep neural networks...
\end{enumerate}

\section{Programming with Our API}
A casual user mostly make function calls to an existing 
manager to pass data and to run the optimization.
More advanced user can configure the manager to achieve more specific requirements.
For example, he can swap out an existing optimization module to achieve a better accuracy or 
a faster speed.
A professional user can implement more modules when he wants to deal with new
material properties that are not handled by our built-in library. In that case,
he needs to know what value the new property is in print materials, he needs to know
how to simulate for the new property, and how to measure error of the new property.

>>>>

\subsection{Optimizer}
\begin{enumerate}
\item MCMC, Simulated Anealing, SPSA
\item Branch and bound (plus clustering of similar configurations)
\item (Optional) reinforcement learning, deep neural networks...
\end{enumerate}
\subsection{Mapper and Reducer}
In some problems such as matching texture colors or local mechanical properties,
the material assignment decision at one location does not influence
decisions made at other locations. The free variables of such problems
are independent of each other. We can express such independency with 
Mapper and Reducer classes. Mapper takes a problem and decomposes
it a set of into independent sub-problems. Reducer
combines solutions to the sub-problems and construct
a complete solution to the origin problem.
\section{Programming with Our API}
A casual user mostly make function calls to an existing 
manager to pass data and to run the optimization.
More advanced user can configure the manager to achieve more specific requirements.
For example, he can swap out an existing optimization module to achieve a better accuracy or 
a faster speed.
A professional user can implement more modules when he wants to deal with new
material properties that are not handled by our built-in library. In that case,
he needs to know what value the new property is in print materials, he needs to know
how to simulate for the new property, and how to measure error of the new property.
